### 2016-07-07 NLO.tex
MSSM K-factors

This output file is in turn invoked by a \texttt{C++} code which evaluates the scalar integrals of the absolute squared matrix amplitudes numerically by using the package \texttt{LoopTools} \cite{Hahn:1998}. Finally the phase space integration is performed by the integration routine "Cuhre" which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}.\\

@@

\subsubsection{$K$-factors for Squark Production in the MRSSM}
A common way to describe next-to-leading order corrections is stating the $K$-factor, which is defined to be the ratio of the complete next-to-leading order cross section $\sigma^{\mathrm{NLO}}$, see eq. \eqref{eq:BVR} and the leading order cross section $\sigma^{\mathrm{LO}}$:
\begin{align}
K(X \to Y) = \frac{\sigma^{\mathrm{NLO}}(X \to Y)}{\sigma^{\mathrm{LO}}(X \to Y)}.
\end{align}
The process in question is described by $X \to Y$.
Figure \ref{fig:1LXsection_fixed_m} shows the $K$-factor for the production of up-squarks in the MRSSM for varying masses of both the squark ($m_{\tilde{g}} = \unit[2000]{GeV}$) and the gluino $m_{\tilde{q}} = \unit[1000]{GeV}$. The mass of the pseudoscalar has been fixed to $m_{\sigma} = \unit[5000]{GeV}$ in both plots. It can be seen that the  $K$-factor increases with increasing squark mass and decreases with increasing gluino mass. Note that the sum of virtual and real corrections gets negative for very light squarks. But this region of parameter space is already excluded phenomenologically.
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msg=2000GeV.png}
\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msq=1000GeV.png}
\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}\tilde{u}$ on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).}\label{fig:1LXsection_fixed_m}
\end{center}
\end{figure}
Calculate uncertainties for multiple points(pdf, scale, integration)

>>>>

This output file is in turn invoked by a \texttt{C++} code which evaluates the scalar integrals of the absolute squared matrix amplitudes numerically by using the package \texttt{LoopTools} \cite{Hahn:1998}. Finally the phase space integration and the integration over $x_1$ and $x_2$ is performed by the integration routine "Cuhre" which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}. The parton density functions are included using \texttt{LHAPDF6}\cite{Buckley:2014ana}\\

@@

\subsubsection{$K$-factors for Squark Production in the MRSSM}
A common way to describe next-to-leading order corrections is stating the $K$-factor, which is defined to be the ratio of the complete next-to-leading order cross section $\sigma^{\mathrm{NLO}}$, see eq. \eqref{eq:BVR} and the leading order cross section $\sigma^{\mathrm{LO}}$:
\begin{align}
K(X \to Y) = \frac{\sigma^{\mathrm{NLO}}(X \to Y)}{\sigma^{\mathrm{LO}}(X \to Y)}.
\end{align}
The process in question is described by $X \to Y$.
Figure \ref{fig:1LXsection_fixed_m} shows the $K$-factor for the production of up-squarks in the MRSSM for varying masses of both the squark ($m_{\tilde{g}} = \unit[2000]{GeV}$) and the gluino $m_{\tilde{q}} = \unit[1000]{GeV}$. The mass of the pseudoscalar has been fixed to $m_{\sigma} = \unit[5000]{GeV}$ in both plots. It can be seen that the  $K$-factor increases with increasing squark mass and decreases with increasing gluino mass. Note that the sum of virtual and real corrections gets negative for very light squarks. But this region of parameter space is already excluded phenomenologically.
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msg=2000GeV.png}
\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msq=1000GeV.png}
\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).}\label{fig:1LXsection_fixed_m}
\end{center}
\end{figure}
Calculate uncertainties for multiple points(pdf, scale, integration)

\subsubsection{$K$-factors for Squark Production in the MSSM}
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.5]{figures/MSSM_uu_susu_Kfactors_msg=2000GeV.png}
\includegraphics[scale=.5]{figures/MSSM_uu_susu_Kfactors_msq=1000GeV.png}
\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}\tilde{u}$, where $\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$, in the MSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).}\label{fig:1LXsection_fixed_m}
\end{center}
\end{figure}
Calculate uncertainties for multiple points(pdf, scale, integration)
\texttt{MadGraph5_aMC@NLO}\cite{Alwall:2014hca}
When generating the code for the process in question, e.g. two protons to $\tilde{u}_L + \tilde{u}_R$, with
\begin{lstlisting}
generate p p > ul ur [QCD] $$go
\end{lstlisting}
the $s$-channel gluinos were omitted as MadGraph does not deal with divergences coming from the gluino in the on-shell limit.

### 2016-07-07 Renormalization.tex
MSSM K-factors

\subsection{The Renormalized Matrix Element}
After having renormalized the matrix element for squark production all UV-divergences are removed. This has been achieved by extending the model file, generated by \texttt{SARAH} with counterterm Feynman rules and the above calculated renormalization constants. The derivation of the counterterm Feynman rules has been performed by the author whereas the implementation into the modelfile was mainly done by Philip Dießner, another member of the group. The renormalization constants for masses and fields are calculated by \texttt{FormCalc} functions like \textsc{MassRC} and \textsc{FieldRC}\cite{FormCalcManual}. Their result has been checked with the above calculated renormalization constants.\\
Auszug von modelfile\\
To keep track of all divergences, the calculation has been performed with the option: \textsc{Dimensions} $\to 0$. This is the only opportunity in \texttt{FormCalc} to really work in $D$ dimensions, i.e. the result contains a quantity $Dminus4$ which equals $-2\epsilon$ in DREG. The absolute matrix element coming from \texttt{FormCalc} is given in terms of scalar integrals, like defined in Appendix \ref{sec:Passarino}.\\
To extract infrared divergences \texttt{LoopTools} has been used. This  tool provides the function \textsc{SetLambda} which can be set to 0, $-1$ or $-2$ to extract the finite part, single pole or double pole of  scalar integrals. This allows for numerically extracting the coefficients of $\epsilon^i$ with $i \in \left\{ 0,-1,-2 \right\}$ of the absolute squared matrix amplitude. The respective poles of $|\mathcal{M}^{\mathrm{V}}_{\mathrm{MRSSM}}(uu \to \tilde{u}_L\tilde{u}_R)|^2$ are shown in figure \ref{fig:MatrixElement}. In addition the tree-level absolute squared matrix amplitude with leading order $\alpha_s$ is compared with its analogue with next-to-leading order $\alpha_s$ and virtual absolute squared matrix amplitude. The latter is  not given analytically. All $|\mathcal{M}|^2$ are color and spin averaged in the final state and summed over in the initial state.
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.5]{figures/MatrixElement_SE_Vertices_Boxes}
\caption{bla}
\end{center}
\end{figure}

>>>>

\subsection{The Renormalized Matrix Element}
After having renormalized the matrix element for squark production all UV-divergences are removed. This has been achieved by extending the model file, generated by \texttt{SARAH} with counterterm Feynman rules and the above calculated renormalization constants. The derivation of the counterterm Feynman rules has been performed by the author whereas the implementation into the modelfile was mainly done by Philip Dießner, another member of the group. The renormalization constants for masses and fields are calculated by \texttt{FormCalc} functions like \textsc{MassRC} and \textsc{FieldRC}\cite{FormCalcManual}. Their result has been checked with the above calculated renormalization constants.\\
\begin{lstlisting}
Auszug von modelfile
\end{lstlisting}
To keep track of all divergences, the calculation has been performed with the option: \textsc{Dimensions} $\to 0$. This is the only opportunity in \texttt{FormCalc} to really work in $D$ dimensions, i.e. the result contains a quantity $Dminus4$ which equals $-2\epsilon$ in DREG. The absolute matrix element coming from \texttt{FormCalc} is given in terms of scalar integrals, like defined in Appendix \ref{sec:Passarino}.\\
To extract infrared divergences \texttt{LoopTools} has been used. This  tool provides the function \textsc{SetLambda} which can be set to 0, $-1$ or $-2$ to extract the finite part, single pole or double pole of  scalar integrals. This allows for numerically extracting the coefficients of $\epsilon^i$ with $i \in \left\{ 0,-1,-2 \right\}$ of the absolute squared matrix amplitude. The respective poles of $|\mathcal{M}^{\mathrm{V}}_{\mathrm{MRSSM}}(uu \to \tilde{u}_L\tilde{u}_R)|^2$ are shown in figure \ref{fig:MatrixElement}. In addition the tree-level absolute squared matrix amplitude with leading order $\alpha_s$ is compared with its analogue with next-to-leading order $\alpha_s$ and virtual absolute squared matrix amplitude. The latter is  not given analytically. All $|\mathcal{M}|^2$ are color and spin averaged in the final state and summed over in the initial state.
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.5]{figures/MatrixElement_SE_Vertices_Boxes}
\caption{bla}
\end{center}
\end{figure}
